Results

### 2018-03-16 02_analysis.Rmd
🎉 ¡Differences between groups! 🎉

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(pander)
library(scales)
library(skimr)
library(janitor)
library(huxtable)
library(here)

@@

print_hux <- function(x) {
  if ("html_document" %in% file_format) {
    print_html(x)
  } else if ("pdf_document" %in% file_format) {
    print_latex(x)
  } else if ("word_document" %in% file_format) {
    print_md(x)
  } else {
    print(x)
  }
}
```

@@

```{r build-models-amount, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
m_amount_crackdown <- 
  stan_glm(amount_donate ~ crackdown,
           data = results, family = gaussian(),
           prior = student_t(df = 1, location = 0),
           prior_intercept = student_t(df = 1, location = 0),
           chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_amount_crackdown_issue <- 
  update(m_amount_crackdown, . ~ . + issue + crackdown * issue)

m_amount_crackdown_issue_funding <- 
  update(m_amount_crackdown, . ~ . + 
           issue + funding + crackdown * issue + crackdown * funding + 
           issue * funding + crackdown * issue * funding)

# Interaction models with extra controls
m_amount_crackdown_full <- 
  update(m_amount_crackdown, . ~ . + 
           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_amount_crackdown_issue_full <- 
  update(m_amount_crackdown_issue, . ~ . + 
           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_amount_crackdown_issue_funding_full <- 
  update(m_amount_crackdown_issue_funding, . ~ . + 
           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

@@

```{r models-table, results="asis"}
huxreg(m_amount_crackdown, m_amount_crackdown_issue, 
       m_amount_crackdown_issue_funding, 
       m_amount_crackdown_full, m_amount_crackdown_issue_full, 
       m_amount_crackdown_issue_funding_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

@@

```{r models-plot}
coefs_amount <- data_frame(model_name = c("Basic model", "Full model"),
                           model = list(m_amount_crackdown_issue_funding,
                                        m_amount_crackdown_issue_funding_full)) %>% 
  mutate(tidy = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
                                         conf.method = "HPDinterval"))) %>% 
  unnest(tidy) %>% 
  left_join(clean_coefs, by = "term") %>% 
  filter(term_clean != "Intercept")

@@

```{r models-predicted}
newdata_conditions <- results %>% 
  expand(nesting(crackdown, issue, funding))

posterior_fit <- posterior_predict(m_amount_crackdown_issue_funding, 
                                   newdata = newdata_conditions,
                                   re.form = NA, draws = 50, seed = BAYES_SEED)

nested_draws <- posterior_fit %>% 
  as_data_frame() %>% 
  gather(id, value) %>% 
  group_by(id) %>%
  nest()

all_posterior_draws <- bind_cols(newdata_conditions, nested_draws) %>% unnest(data)

newdata <- newdata_conditions %>% 
  bind_cols(tidyMCMC(as.mcmc(posterior_fit), conf.int = TRUE, 
                     conf.level = 0.9, conf.method = "HPDinterval"))

ggplot(newdata, aes(y = estimate, x = funding)) + 
  geom_point(data = all_posterior_draws, aes(y = value, x = funding), 
             color = "grey50", size = 1.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
  scale_y_continuous(labels = dollar) +
  labs(x = "Funding", y = "Average amount donated") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  facet_wrap(~ crackdown + issue)
```

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(skimr)
library(janitor)
library(huxtable)
library(here)

@@

print_hux <- function(x) {
  if ("html_document" %in% file_format) {
    print_html(x)
  } else if ("pdf_document" %in% file_format) {
    print_latex(x)
  } else if ("word_document" %in% file_format) {
    print_md(x)
  } else {
    print(x)
  }
}

mcmc_pairwise_diffs <- function(chains) {
  # Calculate the pairwise differences between columns
  # Adapted from http://stackoverflow.com/a/28187446/120898
  pair_names <- outer(colnames(chains), colnames(chains),
                      paste, sep = " − ")
  pairs_to_omit <- which(lower.tri(pair_names, diag = TRUE))

  mcmc_diffs <- outer(1:ncol(chains), 1:ncol(chains),
                      function(x, y) chains[,x] - chains[,y]) %>% 
    magrittr::set_colnames(pair_names) %>% 
    select(-pairs_to_omit)

  return(mcmc_diffs)
}

tidy_diffs <- function(diffs_pairs) {
  diffs_pairs %>% 
    gather(pair, value) %>% 
    group_by(pair) %>% 
    summarise(mean = mean(value),
              median = median(value),
              q2.5 = quantile(value, probs = 0.025),
              q5 = quantile(value, probs = 0.05),
              q25 = quantile(value, probs = 0.25),
              q75 = quantile(value, probs = 0.75),
              q95 = quantile(value, probs = 0.95),
              q97.5 = quantile(value, probs = 0.975),
              p.greater0 = mean(value > 0),
              p.less0 = mean(value < 0))
}
```

@@

```{r build-models-amount, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
m_amount_c <- stan_glm(amount_donate ~ crackdown,
                       data = results, family = gaussian(),
                       prior = student_t(df = 1, location = 0),
                       prior_intercept = student_t(df = 1, location = 0),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)

m_amount_cif <- update(m_amount_c, . ~ . + 
                         issue + funding + crackdown * issue + crackdown * funding + 
                         issue * funding + crackdown * issue * funding)

# Interaction models with extra controls
m_amount_c_full <- update(m_amount_c, . ~ . + 
                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_amount_ci_full <- update(m_amount_ci, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

@@

```{r models-table, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

@@

```{r models-plot}
coefs_amount <- data_frame(model_name = c("Basic model", "Full model"),
                           model = list(m_amount_cif,
                                        m_amount_cif_full)) %>% 
  mutate(tidy = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
                                         conf.method = "HPDinterval"))) %>% 
  unnest(tidy) %>% 
  left_join(clean_coefs, by = "term") %>% 
  filter(term_clean != "Intercept")

@@

The Stan people really really don't like `posterior_linepred()`, since it throws away a lot of the uncertainty that comes from actually getting a posterior distribution. But this approach here mirrors using `predict()` to combine all the coefficients and intercept terms in a regular frequentist linear model and it's probably appropriate for this situation because all the coefficients are actually linked together behind the scenes and create group mean estimates. If I use the full force of `posterior_predict()`, I add more uncertainty with each added coefficient (so in a 2×2×2 version, the 8th condition is actually the sum of all 8 coefficients, which means it gets 8 levels of uncertainity, which is probably excessive). But we do it both ways too, just to be on the safe side.

```{r amount-median-c}
newdata_conditions_c <- results %>% expand(nesting(crackdown))

chains_fitted_c <- posterior_linpred(m_amount_c, 
                                   newdata = newdata_conditions_c)

# posterior_fit <- posterior_predict(m_amount_c, 
#                                    newdata = newdata_conditions_c,
#                                    draws = 50, seed = BAYES_SEED)

coef_summary_c <- newdata_conditions_c %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_c), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

# newdata <- newdata_conditions %>% 
#   bind_cols(tidyMCMC(as.mcmc(posterior_fit), estimate.method = "median",
#                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_amount_c <- ggplot(coef_summary_c, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

```{r amount-median-ci}
newdata_conditions_ci <- results %>% expand(nesting(crackdown, issue))

chains_fitted_ci <- posterior_linpred(m_amount_ci, 
                                   newdata = newdata_conditions_ci)

coef_summary_ci <- newdata_conditions_ci %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_ci), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_amount_ci <- ggplot(coef_summary_ci, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_blue) + 
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue)
```

```{r amount-median-cif}
newdata_conditions_cif <- results %>% expand(nesting(crackdown, issue, funding))

chains_fitted_cif <- posterior_linpred(m_amount_cif, 
                                   newdata = newdata_conditions_cif)

coef_summary_cif <- newdata_conditions_cif %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_cif), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_amount_cif <- ggplot(coef_summary_cif, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_red) +
  scale_y_continuous(labels = dollar) +
  labs(x = NULL, y = "Median amount donated") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue + funding)
```

```{r plot-all-amount-medians, fig.width=8, fig.height=6}
((plot_amount_c + 
   labs(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown around each point")) / 
   plot_amount_ci) | plot_amount_cif
```

## Differences in medians

```{r amount-diffs-c}
diffs_coef_pairs_c <- chains_fitted_c %>% 
  as_data_frame() %>% 
  magrittr::set_colnames(levels(newdata_conditions_c$crackdown)) %>% 
  mcmc_pairwise_diffs()

diffs_coef_pairs_detail_c <- tidy_diffs(diffs_coef_pairs_c)

pairs_plot_data_c <- diffs_coef_pairs_c %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

plot_diffs_c <- ggplot() + 
  geom_density(data = pairs_plot_data_c, aes(x = value),
               fill = ngo_green, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_c, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_c, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)
```

```{r amount-diffs-ci}
# Nest each fitted chain into a single row that corresponds to each newdata_condition
chains_nested_ci <- chains_fitted_ci %>% 
  as_data_frame() %>% 
  mutate(id = 1:n()) %>% 
  gather(condition, value, -id) %>% 
  group_by(condition) %>% 
  nest()

# Add the fitted chains to the conditions, spread the main crackdown condition
# into two columns, then nest everything by issue
all_chains_ci <- bind_cols(newdata_conditions_ci, chains_nested_ci) %>% 
  unnest(data) %>% 
  select(-condition) %>% 
  group_by(issue) %>% 
  spread(crackdown, value) %>% 
  select(-id) %>% 
  nest()

# All the pairwise differences in a single data frame, grouped by issue
pairs_conditions_ci <- all_chains_ci %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))

# Extract coefficient details and plot data
diffs_coef_pairs_detail_ci <- pairs_conditions_ci %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs)

pairs_plot_data_ci <- pairs_conditions_ci %>% 
  select(issue, diffs_coef_pairs) %>% 
  unnest(diffs_coef_pairs) %>%
  gather(pair, value, -issue) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

plot_diffs_ci <- ggplot() + 
  geom_density(data = pairs_plot_data_ci, aes(x = value),
               fill = ngo_blue, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_ci, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_ci, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + pair)
```

```{r amount-diffs-cif}
# Nest each fitted chain into a single row that corresponds to each newdata_condition
chains_nested_cif <- chains_fitted_cif %>% 
  as_data_frame() %>% 
  mutate(id = 1:n()) %>% 
  gather(condition, value, -id) %>% 
  group_by(condition) %>% 
  nest()

# Add the fitted chains to the conditions, spread the main crackdown condition
# into two columns, then nest everything by issue
all_chains_cif <- bind_cols(newdata_conditions_cif, chains_nested_cif) %>% 
  unnest(data) %>% 
  select(-condition) %>% 
  group_by(issue, funding) %>% 
  spread(crackdown, value) %>% 
  select(-id) %>% 
  nest()

# All the pairwise differences in a single data frame, grouped by issue
pairs_conditions_cif <- all_chains_cif %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))

# Extract coefficient details and plot data
diffs_coef_pairs_detail_cif <- pairs_conditions_cif %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs)

pairs_plot_data_cif <- pairs_conditions_cif %>% 
  select(issue, funding, diffs_coef_pairs) %>% 
  unnest(diffs_coef_pairs) %>%
  gather(pair, value, -issue, -funding) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

plot_diffs_cif <- ggplot() + 
  geom_density(data = pairs_plot_data_cif, aes(x = value),
               fill = ngo_red, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_pairs_detail_cif, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_cif, aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + funding + pair)
```

```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
((plot_diffs_c + 
   labs(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
   plot_diffs_ci) | plot_diffs_cif
```

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown (median)` = median, 
         `P(m > 0)` = p.greater0, `P(m < 0)` = p.less0) %>% 
  pandoc.table(missing = "—", 
               caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions')
```
